### 2016-03-23 paper.tex
Revise design experiment section including several new references

Our experiment involved a team of eleven undergraduate students and a
faculty mentor.  The students majors include Computer Science, English
(Creative Writing), Philosophy, Telecommunications (Audio Production),
and Art (Animation).
Each student earned three credit hours for the experience during a fifteen-week
semester,
working together in a studio space for two hours each Monday, Wednesday,
and Friday.
The team collectively agreed upon three primary goals for the design
experiment in the cultural-narration genre:
to use narrative as the primary form of player feedback;
to teach cultural empathy;
and to use technology to address complications of analog implementations.

After these goals were defined, the team figured out a game concept, and 
developed it throughout three iterations.
The deadlines for each iteration provided the team a chance to reflect on both
the project itself and on our methodology.  Each iteration was tested at
\textit{the library branch}, providing valuable data for which directions we
should bring the project.  We also had reflective meetings in which we 
discussed what worked about our methodology, and what should change.  During
the first two iterations, we organized our tasks using \textit{story mapping}.
However, we realized during our second reflective meeting that it might be
better to switch to Scrum.

We used JavaFX for rough prototyping, which some of the developers had used
before, and then moved to \textit{PlayN}, a cross-platform library that allowed
us to build both for Java and HTML.
Our writers and artist continually developed and improved assets for the game,
learning how to bring them into the game easily.  The writers also developed a
methodology for workshopping each other to make sure the narrative was 
developed and had a consistent voice.

Most of the team played vital roles in both the research side of the game and
the development side of the game.  The writers, for example, did extensive
research on different cultures and monsters as well as writing in a way that
would be easy for kids to read.  Writers and developers were involved in the
playtesting as well, and gained valuable insight on what the kids needed and
wanted.

We also invited guests to join us during our regular meeting times to talk about
their experiences with games, monsters, and children's literacy.  One of our
guests gave us valuable insight on what monsters mean to people and how they are
influenced by culture.

>>>>

Our experiment involved a team of eleven undergraduate students and a
faculty mentor.  The students majors include Computer Science, English
(Creative Writing), Philosophy, Telecommunications (Audio Production),
and Art (Animation).
Each student earned three credit hours for the experience during a fifteen-week
semester,
working together in a studio space for two hours each Monday, Wednesday,
and Friday.
% In future version, cite the TOCE paper
The team collectively agreed upon three primary goals for the design
experiment in the cultural-narration genre:
to use narrative as the primary form of player feedback;
to teach cultural empathy;
and to use technology to address complications of analog implementations.

Given these goals, the team proceeded with an incremental and
iterative approach to game design and development, each iteration
producing an executable release in accordance with best practices of
agile software development~\citep[see, for
example,][]{Cockburn2006,Keith2010}.  Each iteration was tested at
\textit{[the library branch]}, providing valuable feedback to the
team.  Each iteration concluded with a retrospective
meeting~\citep{Kerth2001}, which provided an opportunity for the
team's reflective practice~\citep{Schon1984}.
The results of these retrospectives included large and small changes
to the team's methodology, including a transition from
story mapping~\citep{Patton2014} to Scrum~\citep{Schwaber2013}.
In addition to paper prototypes, the team 
developed prototypes using JavaFX, PlayN, and Polymer, 
all of which allow for HTML5 Web deployment.
Game images and stories were inspired by the team's research on monsters
from world cultures, which included both research sources
(such as \citet{Cohen1996}) and children's books (especially
\citet{Steer2008} and \citet{Stowell2013}).
The team also consulted with local university experts on
games, monsters, world cultures, and literacy.
